### 2023-09-07 sections/2-methods.tex
one more typo

We define a \emph{cluster} as a set of points with a \emph{center}, a \emph{radius}, and an approximation of the \emph{local fractal dimension}.
The \emph{center} is the geometric median of a sample of points in the \emph{cluster}, and so it is a real data point.
The \emph{radius} is the maximum distance from any point in the cluster to the \emph{center}.
We estimate \emph{local fractal dimension} at the scale of the cluster radius and half the cluster radius.
Each cluster (unless it is a leaf cluster) has two child clusters in much the same way that a node in a binary tree has two child nodes.
We define the \emph{metric entropy} $\mathcal{N}_{\hat{r_c}}(D)$ of a data set $D$ under a hierarchical clustering scheme as a refinement of~\cite{yu2015entropy}, where metric entropy for a given cluster radius $r_c$ was the number of clusters of radius $r_c$ needed to cover all data.
Here, we use a hierarchical, divisive clustering approach, but with early stopping criteria; clusters which satisfy a user-specified stopping criterion (e.g. a specified cardinality or radius) are not further split.
Since we frame the asymptotic complexity of $\rho$-NN search in terms of the number of leaf clusters, the \emph{metric entropy} is best thought of in terms of the number of leaf clusters.

>>>>

We define a \emph{cluster} as a set of points with a \emph{center}, a \emph{radius}, and an approximation of the \emph{local fractal dimension}.
The \emph{center} is the geometric median of a sample of points in the \emph{cluster}, and so it is a real data point.
The \emph{radius} is the maximum distance from any point in the cluster to the \emph{center}.
We estimate \emph{local fractal dimension} at the scale of the cluster radius and half the cluster radius.
Each cluster (unless it is a leaf cluster) has two child clusters in much the same way that a node in a binary tree has two child nodes.
We define the \emph{metric entropy} $\mathcal{N}_{\hat{r_c}}(X)$ of a data set $X$ under a hierarchical clustering scheme as a refinement of~\cite{yu2015entropy}, where metric entropy for a given cluster radius $r_c$ was the number of clusters of radius $r_c$ needed to cover all data.
Here, we use a hierarchical, divisive clustering approach, but with early stopping criteria; clusters which satisfy a user-specified stopping criterion (e.g. a specified cardinality or radius) are not further split.
Since we frame the asymptotic complexity of $\rho$-NN search in terms of the number of leaf clusters, the \emph{metric entropy} is best thought of in terms of the number of leaf clusters.
